Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-04-10 paper.qmd
Found the way to projected the models
Saved data for other methods as well

# write_rds(distance_df_small_edges, "data/five_gau_clusters/tsne_model.rds")
```

@@

# write_rds(distance_df_small_edges, "data/five_gau_clusters/umap_model.rds")
```

@@

# write_rds(distance_df_small_edges, "data/five_gau_clusters/pacmap_model.rds")
```

>>>>

# write_rds(distance_df_small_edges, "data/five_gau_clusters/tsne_wireframe.rds")
# write_rds(df_b, "data/five_gau_clusters/tsne_model.rds")
```

@@

# write_rds(distance_df_small_edges, "data/five_gau_clusters/umap_wireframe.rds")
# write_rds(df_b, "data/five_gau_clusters/umap_model.rds")
```

@@

# write_rds(distance_df_small_edges, "data/five_gau_clusters/pacmap_wireframe.rds")
# write_rds(df_b, "data/five_gau_clusters/pacmap_model.rds")
```
